Optimizing the Robotics Closet

### 2018-12-05 paper.tex
symbol fixes. tried to lower usage of i, j, l

shelf $s$ is represented as an ordered triple $(d, L, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $L$ is the length of the shelf, and

@@

Each item is represented with an ordered triple $(l, p, s)$, where $l$ is the length

@@

unit of height. As a preprocessing step, minimize the length. Since we cannot always

@@

$$l = \min(a, b)$$

@@

$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. \\

@@

\\

@@

\item $\sum_{j = 1}^{m}w_{ij}l^i_j \leq l^s_i, 1 \leq i \leq n$.
\item $\sum_{j = 1}^{n}w_{ji} = 1, 1 \leq i \leq m$.
\item $\sum_{j = 1}^{l}c_{ji} = 1, 1 \leq i \leq k$.

@@

\textbf{Explanation of Constraints:}
\begin{enumerate}
\item The sum the lengths of all of the items on a given shelf must be less than or equal to
  the maximum length that the shelf can support. We multiply by $w_{ji}$ so that
  items not included on the shelf are not counted.
\item Each column of $W$ can only have one $1$, because we cannot put an item
  on two shelves simultaneously. Since each row represents a shelf, we simply
  traverse the whole column and ensure its sum is exactly $1$. Notice that if
  we had put $\leq 1$, the constraint would have been invalid because then
  no items would have been included. Thus, this constraint implicitly enforces
  the constraint that every item be included.
\item Each column of $C$ can only have one $1$ because all items belonging to
  a subsystem must be in the same connected component, and therefore a subsystem
  can be in exactly one connected component. Similarly to constraint 2, summing
  this and ensuring that the sum is 1 enforces the idea that every subsystem is
  included.
\item The intuition behind this constraint is that either all items belonging
  to a subsystem are in the same connected component, or none are. Thus, we
  use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not.
\end{enumerate}

>>>>

shelf $s$ is represented as an ordered triple $(d, L^{shelf}, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $L^{shelf}$ is the length of the shelf, and

@@

Each item is represented with an ordered triple $(L^{item}, p, s)$, where $L^{item}$ is the length

@@

unit of height. As a pre-processing step, minimize the length. Since we cannot always

@@

$$L^{item} = \min(a, b)$$

@@

$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. 

@@

@@

\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n_0$ ($n_0 = $ number of shelves).
\item $\sum_{i = 1}^{n}w_{ij} = 1, $ for every $1 \leq j \leq m$ ($m = $ number of items).
\item $\sum_{j = 1}^{l}c_{ji} = 1, $ for every $1 \leq i \leq k$.

@@

\textbf{Explanation of Constraints:}
\begin{enumerate}
\item The sum the lengths of all of the items on a given shelf must be less than or equal to
  the maximum length that the shelf can support. We multiply by $w_{ji}$ so that
  items not included on the shelf are not counted.
\item Each column of $W$ can only have one $1$, because we cannot put an item
  on two shelves simultaneously. Since each row represents a shelf, we simply
  traverse the whole column and ensure its sum is exactly $1$. Notice that if
  we had put $\leq 1$, the constraint would be invalid because then
  no items could have been included. Thus, this constraint implicitly enforces
  the constraint that every item be included.
\item Each column of $C$ can only have one $1$ because all items belonging to
  a subsystem must be in the same connected component, and therefore a subsystem
  can be in exactly one connected component. Similarly to constraint 2, summing
  this and ensuring that the sum is 1 enforces the idea that every subsystem is
  included.
\item The intuition behind this constraint is that either all items belonging
  to a subsystem are in the same connected component, or none are. Thus, we
  use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not.
\end{enumerate}
